\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.25in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------
\begin{document}
\begin{center}
\textbf{\Huge Shreyas Kowshik \\ }  
\indent \hfill \break
\indent C 415 , Nehru Hall, \hfill Email-id : \textbf{shreyaskowshik@iitkgp.ac.in} \\
\indent Indian Institute of Tehnology, Kharagpur \hfill Mobile No.: \textbf{9892425461} \\
\indent West Bengal, INDIA - 721302  \hfill Github:\url{https://github.com/shreyas-kowshik/} \\
\end{center}

\hspace{0.5cm}\\[-0.2cm]
\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ 
%\begin{table}[ht!]
%\begin{center}

\indent \begin{tabular}{ l @{\hskip 0.25in} l @{\hskip 0.25in} l @{\hskip 0.25in} l @{\hskip 0.25in} l }
\hline
\textbf{Education} & \textbf{Institute} & \textbf{Year} & \textbf{CPI / \%} \\
\hline
Integrated Msc.:\\
{Mathematics And Computing} & IIT Kharagpur  & 2017- Till date & \textbf{9.47 / 10} \\ \\
12th & Thakur Vidya Mandir, Mumbai & 2015 - 2017 & \textbf{96.31 \%}\\ \\
10th & Thakur Public School, Mumbai & 2015 & \textbf{97.5 \%}\\
\hline
\end{tabular}
%\end{center}
%\end{table}
\\ \hfill \break \\

\resheading{\textbf{RESEARCH PAPERS} }\\[\lsep]

\begin{itemize}
\item \textbf{Traffic Sign Detection Using Hybrid Features And CNN} \\
\emph{October 2018}
	\begin{itemize}
	\item Proposed a unique Branch CNN architecture to reduce the model parameters manifold.
	\item Submitted at the 8th \textbf{ICPRAM}, 2019.
	\end{itemize}
\end{itemize}

\resheading{\textbf{MAJOR PROJECTS} }\\[\lsep]

\begin{itemize}
\item \textbf{Autonomous Car} \hspace{0.5cm} \\ 
\emph{Autonomous Ground Vehicle Research Group}\\
 \emph{(Guide: Prof. Debashish Chakravarty																							
, March'18 - till date)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Working to convert Mahindra E2O into a fully operational self driving car
	\item Experimented with CNN architectures using primitive image feartures like HOG and SURF to reduce computation size of architectures.
	\item Worked on the Frenet Planner for efficient highway trajectory maneuvers.
.
	\item Research Areas: Path Planning,Computer Vision.
	\end{itemize} 

\item \textbf{Eklavya 4.0} \\ 
\emph{Autonomous Ground Vehicle Research Group} \hspace{0.5cm}
{}\\
 \emph{(Guide: Prof. Debashish Chakravarty																							
, April'18 - June'18} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Adjuged \textbf{2nd} in \textbf{Intelligent Ground Vehicle Competition,2018}.
	\item Worked on \textbf{robot-localization},\textbf{Timed Elastic Band} ROS local planner,\textbf{lane detection} and \textbf{waypoint navigation}.
	\item Implemented \textbf{SVM} based \textbf{object-detection} and \textbf{lane detection} using \textbf{pixel-clustering}.
	\end{itemize} 

\item \textbf{Image Dehazing Using Dark Channel Prior} \hspace{0.5cm} \url{https://github.com/dishank-b/dark-channel-prior}

	\emph{Image Processing Term Project}
	\begin{itemize}\itemsep \isep
	\item Implemented the paper '\textbf{Single Image Dehazing Using Dark Channel Prior}'.
	
	\item Used a \textbf{guided filter} to refine the transmisison map to obtain better quality images. 
	\end{itemize} 
	
\item \textbf{Kharagpur Robosoccer Student's Group} \\ 
 \emph{Guide: Prof. Jayanta Mukhopadhyay										
, April'18 - June'18} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Worked on the software stack for soccer playing robots in robocup.
	\item Implemented a \textbf{fuzzy-logic},based passaing mechanism.
	\item Wrote a RRT* planner from scratch in C++. \\ \\
	\end{itemize} 
\end{itemize}

\hspace{0.5cm}\\[-0.2cm]

\hspace{0.5cm}\\[-0.2cm]

\resheading{\textbf{SIDE PROJECTS AND PAPER IMPLEMENTATIONS} }\\[\lsep]
\begin{itemize}
\item \textbf{Reinforcement Learning Stack} \hspace{1.0cm} \url{https://github.com/shreyas-kowshik/RL-algorithms}
	\begin{itemize}\itemsep \isep
	\item Implementation of RL algorithms on Open-AI Gym Environments.
	
	\item Implemented \textbf{Dynamic Programming}, \textbf{Monte Carlo}, \textbf{Temporal Difference} Learning,\textbf{Deep Q-learning} and \textbf{Policy Gradient} algorithms. 
	\end{itemize}
	
\item \textbf{Deep Convolutional Generative Adversarial Networks} \hspace{0.5cm} \url{https://github.com/shreyas-kowshik/Generative-Models-Tensorflow} \\
\emph{Paper Implementation}

\end{itemize}

\resheading{\textbf{AWARDS AND ACHIEVEMENTS} }\\[\lsep]
\begin{itemize}

\item \noindent \textbf{2nd Runner Up}, Image Processing Event,Fortress, Kshitij,2017 
\item \noindent \textbf{Gold Medal,Indian National Chemistry Olympiad} : Among the top 35 students nationally to be selected for the training-cum-selection camp for the International Chemistry Olympiad(IChO) 2017.
\item \noindent \textbf{KVPY 2017. All India Rank 18} :
One of the presitigious examination initiated by Department of Science and Technology, Government of India
\item \noindent \textbf{3rd Overall,HSC Board} : 12th Std. State Board Examination
\end{itemize}

\hspace{0.5cm}\\[-0.2cm]
\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Languages} C, C++, Python, Matlab, {\LaTeX{}} \\
\textbf{Libraries and Tools} Tensorflow,OpenCV, ROS, Octave \\
\textbf{Field of Interest} Computer Vision, Path Planning, Machine Learning,Reinforcement Learning. \\
\end{itemize}

\end{document}
